### 2015-12-03 paper.tex
Reference the Reynolds number table
Discuss strut drag results and cite Rawlings thesis; resolves #22 and resolves #7

Data collection runs were separated into individual tows, for which all
independent variables---tow speed, tip speed ratio, velocity probe
position---were held constant. These runs were grouped into logical test matrix
``sections,'' in which typically a single independent variable was varied. Test
matrix section names and descriptions are provided in the \texttt{README.md}
file of the experimental data and code repository \cite{Bachant2015-RM2-data}.

@@

We see that strut drag losses increase with tip speed ratio to the power 2--3,
which makes streamlined struts much more important for low solidity turbines,
given the inverse correlation between solidity and $\lambda_0$.

@@

>>>>

Data collection runs were separated into individual tows, for which all
independent variables---tow speed, tip speed ratio, velocity probe
position---were held constant. These runs were grouped into logical test matrix
``sections,'' in which typically a single independent variable was varied. Test
matrix section names and descriptions are provided in the \texttt{README.md}
file of the experimental data and code repository \cite{Bachant2015-RM2-data}.
Tow speed and their corresponding turbine diameter and blade chord Reynolds
numbers are presented in Tab.~\ref{tab:re}.

@@

Performance curves for the rotor with both NACA 0021 and cylindrical struts are
shown in Fig.~\ref{fig:perf-covers}. As expected, the high drag cylindrical
struts reduce performance dramatically, which worsens as $\lambda$ increases.
This is in accordance with the measurements of Rawlings \cite{Rawlings2008},
though the strut losses in this case are larger due to the very high drag profile.

Measurements for the power coefficient contributions of the strut drag losses
are presented in Fig.~\ref{fig:no-blades} for NACA 0021 and cylindrical
struts---both in towed and stationary conditions. These are computed in the same
fashion as the curves in Fig.~\ref{fig:cp-curves}, but with the blades removed.
We see that strut drag losses increase with tip speed ratio to the power 2--3,
which makes streamlined struts much more important for low solidity turbines,
given the inverse correlation between solidity and $\lambda_0$
\cite{Templin1974}.

@@

Strut drag losses do not change much for the streamlined NACA 0021 struts in the
towed versus stationary configuration. However, for the cylindrical struts,
losses increase significantly when towed and operating in the mid range of tip
speed ratios. With respect to numerical modeling, these measurements will allow
support struts to be simulated without blades, to isolate and evaluate the
ability to predict these losses independent of the blade loading.
